---
title: "Project"
output: html_document
date: '2022-10-05'
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(tidyr)
library(randomForest)
library(car)

```

correlated tree models. conditional
linear mix models.

```{r cars}
df <- read.csv("demototal.csv")

df <- df %>%
         filter(pregnant_week < 40,age < 39)

df <- df %>% 
  mutate(
    duration = duration/60,
    awake = awake/60,
    light = light/60,
    rem = rem/60,
    deep = deep/60,
    total = total/60,
    Obesity = as.factor(Obesity),
    over30 = as.factor(over30),
    trimester = case_when(pregnant_week <= 13 ~ '1',
                          pregnant_week <= 26 ~ '2',
                          pregnant_week > 26 ~ '3')
  )
```



```{r}
mem1 <- lmer(hr_average ~ duration*pregnant_week + (1|id) + (1|Obesity) +(1|over30), data = df)
```
```{r}
summary(mem1)
```

```{r}
mem2 <- lmer(hr_average ~ awake*light*rem*deep*pregnant_week + (1|id) + (1|Obesity) +(1|over30), data = df)
summary(mem2)
```

```{r}
mem3 <- lmer(hr_average ~ bedtime_start_delta*bedtime_end_delta + (1|id) + (1|Obesity) +(1|over30), data = df)
summary(mem3)
```
```{r}
mem4 <- lmer(hr_average ~ bedtime_start_delta*pregnant_week + (1|id) + (1|Obesity) +(1|over30), data = df)
summary(mem4)
```
```{r}
mem5 <- lmer(hr_average ~ onset_latency*midpoint_time + (1|id) + (1|Obesity) +(1|over30), data = df)
summary(mem5)
```
```{r}
mem6 <- lmer(hr_average ~ temperature_deviation*temperature_trend_deviation+ (1|id) + (1|Obesity) +(1|over30), data = df)
summary(mem6)
```
significant factor: pregnant week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation


```{r}
mem7 <- lmer(hr_average ~ temperature_delta+ (1|id) + (1|Obesity) +(1|over30), data = df)
summary(mem7)
```

significant factor: pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta

```{r}
newdf <- df %>%
  select(rmssd,pregnant_week, bedtime_start_delta, 
         temperature_deviation, temperature_trend_deviation, 
         temperature_delta,duration,awake,light,
         rem,deep,age,onset_latency,midpoint_time,
         efficiency,restless,breath_average,id,Obesity,over30)
```

```{r}
fmem <- lmer(rmssd ~. + (1|id) + (1|Obesity) +(1|over30), data = newdf)
summary(fmem)
```



```{r}
newdf %>% drop_na()
```

```{r}
newdf=na.omit(newdf)
rmssd.rf<- randomForest (rmssd~.,data=newdf,importance = TRUE,
         ntree=1000)
```

```{r}
print(rmssd.rf)
```
```{r}
importance(rmssd.rf)
```
```{r}
varImpPlot(rmssd.rf)
```

2.


```{r}
newdf <- split(df, f = df$over30)
```

```{r}
younger <- newdf$`0`
older <- newdf$`1`
```

```{r}
youngerdf <- younger %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta,duration,awake,light,rem,deep,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
youngertmp <- younger %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, duration,awake,light,rem,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
younglm <- lm(rmssd ~ .,data = youngertmp)
summary(younglm)
```

```{r}
youngerdf %>% drop_na()
```

```{r}
youngerdf=na.omit(youngerdf)
rmssdy.rf<- randomForest (rmssd~.,data=youngerdf,importance = TRUE,
         ntree=1000)
```

```{r}
print(rmssdy.rf)
```

```{r}
importance(rmssdy.rf)
```

```{r}
varImpPlot(rmssdy.rf)
```


```{r}
olderdf <- older %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta,duration,awake,light,rem,deep,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
olderdf %>% drop_na()
```

```{r}
olderdf=na.omit(olderdf)
rmssdolder.rf<- randomForest (rmssd~.,data=olderdf,importance = TRUE,
         ntree=500)
```

```{r}
print(rmssdolder.rf)
```

```{r}
importance(rmssdolder.rf)
```

```{r}
varImpPlot(rmssdolder.rf)
```
     Younger people should care more about their bed starting time, older people should care more about their sleep duration. 
     

```{r}
obesitydf <- split(df, f = df$Obesity)
```

```{r}
obesity <- obesitydf$`0`
nobesity <- obesitydf$`1`
```

```{r}
obesity <- obesity %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta,duration,awake,light,rem,deep,age,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
obesity %>% drop_na()
```

```{r}
obesity=na.omit(obesity)
rmssdobe.rf<- randomForest (rmssd~.,data=obesity,importance = TRUE,
         ntree=1000)
```

```{r}
print(rmssdobe.rf)
```

```{r}
importance(rmssdobe.rf)
```

```{r}
varImpPlot(rmssdobe.rf)
```

```{r}
nobesity <- nobesity %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta,duration,awake,light,rem,deep,age,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
nobesity %>% drop_na()
```

```{r}
nobesity=na.omit(nobesity)
rmssdnobe.rf<- randomForest (rmssd~.,data=nobesity,importance = TRUE,
         ntree=1000)
```

```{r}
print(rmssdnobe.rf)
```

```{r}
importance(rmssdnobe.rf)
```

```{r}
varImpPlot(rmssdobe.rf)
varImpPlot(rmssdnobe.rf)
```

non Obesity deep sleep, obesity breath average.




```{r}
trimester <- split(df,df$trimester)
first <- trimester$`1`
sec <- trimester$`2`
third <- trimester$`3`
```



```{r}
seconddf <- sec %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta,duration,awake,light,rem,deep,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
seconddf %>% drop_na()
```

```{r}
seconddf=na.omit(seconddf)
rmssdsec.rf<- randomForest (rmssd~.,data=seconddf,importance = TRUE,
         ntree=1000)
```

```{r}
print(rmssdsec.rf)
```

```{r}
importance(rmssdsec.rf)
```

```{r}
varImpPlot(rmssdsec.rf)
```

```{r}
thirdf <- third %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, temperature_delta,duration,awake,light,rem,deep,onset_latency,midpoint_time,efficiency,restless,breath_average)
```

```{r}
thirdf %>% drop_na()
```

```{r}
thirdf=na.omit(thirdf)
rmssdthird.rf<- randomForest (rmssd~.,data=thirdf,importance = TRUE,
         ntree=1000)
```

```{r}
cor(thirdf)
```

```{r}
print(rmssdthird.rf)
```

```{r}
importance(rmssdthird.rf)
```

```{r}
varImpPlot(rmssdsec.rf)
varImpPlot(rmssdthird.rf)
```

week3


```{r}
age <- df %>%
  select(rmssd,pregnant_week, bedtime_start_delta, temperature_deviation, temperature_trend_deviation, duration,awake,light,rem,onset_latency,deep,midpoint_time,efficiency,restless,breath_average)
```

```{r}
age %>% drop_na()
```

```{r}
age=na.omit(age)
age.rf<- randomForest (rmssd~.,data=age,importance = TRUE,
         ntree=500)
```

```{r}
print(age.rf)
```

```{r}
importance(age.rf)
```

```{r}
varImpPlot(rmssdobe.rf)
varImpPlot(rmssdnobe.rf)
```

```{r}
varImpPlot(rmssdy.rf)
varImpPlot(rmssdolder.rf)
```
```{r}
varImpPlot(rmssdsec.rf)
varImpPlot(rmssdthird.rf)
```
```{r}
summary(df$rmssd)
```




